---
title: "Timepoint Scatter Plots"
author: "Matthew Salaciak"
date: "10/15/2020"
output: html_document
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(Matrix)
library(tidyverse)
library(RCurl)
library(cowplot)
library(pheatmap)
library(clusterProfiler)
library("org.Dm.eg.db",character.only = TRUE)
library(DOSE)

library(plotly)

load(file="Data4Rmd.RData")
load(file="plotlists.RData")
library(htmlwidgets)
library(htmltools)
library(ggrastr)
library(ExPanDaR)


```


## Including Plots

Scatter plots comparing clusters but at different time points with hopes to identify obvious outliers.

The ouliers are selected by comparing the natural log transformed average gene expression from one time point to the other.

If the difference between gene expression is greater than 0.9, this is considered an outlier and the gene is labeled and colored.

For example, if one scatter plot is comparing Timepoint 1 vs 2, and the outlier is on the Y-axis (Timepoint 2), it can be interpreted as 
that specific gene has a higher expression in Timepoint 2 (Y-axis) compared to Timepoint 1 (X-axis).


## UMAP comparing timepoints for reference 

Please note that the cluster ID's are still being further investigated in order to determine specific subsets.
``` {r, echo=FALSE, fig.width = 8}
for (k in 1:6){
print(plotlists[[k]])
}
```


``` {r pressure, echo=FALSE, warning=FALSE}

Cluster.names <- list("CD14 Mono 1", "CD14 Mono 2", "CD4 TCM", "CD4 Naive","CD14 Mono 3"," CD8 t-cell 1","CD8 t-cell 2", "CD8 t-cell 3", "CD14 Mono 4"
		,"NK" , "CD16 Mono " ,"B Cell" ,"CD8 TEM","CD14 Mono 5" ,"cpDC","CD14 Mono 6", "CD4 Treg" ,"CD8 Exhausted" ,"CD8 Teff" ,"pDC")


for (i in 1:20) {

dummyDF <-fileNames[[i]]
clusterID <-Cluster.names[[i]]

dummyDF <- dummyDF %>%
  rename(
    time_1 = 1,
    time_2 = 2,
    time_3 = 3,
    time_4 = 4,
    time_5 = 5,
    time_6 = 6,
    )
timePointCol <- list(dummyDF$time_1,
                     dummyDF$time_2,
                     dummyDF$time_3,
                     dummyDF$time_4,
                     dummyDF$time_5,
                     dummyDF$time_6)

for(j in 1:5) {

  time_x <-timePointCol[[j]]
  time_y<-timePointCol[[j+1]]
  
highlight_df <- dummyDF %>% mutate(Difference = time_y - time_x) %>%
             filter(abs(Difference) >=0.9)

timePointColHL <- list(highlight_df$time_1,
                     highlight_df$time_2,
                     highlight_df$time_3,
                     highlight_df$time_4,
                     highlight_df$time_5,
                     highlight_df$time_6)


 time_x_hl <-timePointColHL[[j]]
  time_y_hl <-timePointColHL[[j+1]]


  clusterPlot<-ggplot(dummyDF, aes(x = time_x, y=time_y)) +  ggtitle(paste(clusterID,", Timepoint", j ,"vs.",  j+1)) +
    geom_point_rast(size=1,alpha=0.7)   +
    geom_point_rast(highlight_df, mapping = aes(x=time_x_hl,y=time_y_hl, color=gene),size=1.3)

  print(clusterPlot + theme(panel.background = element_rect(fill = "white", colour = "grey50"),legend.text=element_text(size=8),
                            legend.title=element_text(size=10), plot.title = element_text(size =12))  +labs(x= (paste("Timepoint ",j)), y = (paste("Timepoint ",j +1))))




}
rm(timePointCol)
rm(dummyDF)
rm(clusterPlot)
rm(timePointColHL)
rm(highlight_df)
rm(time_x)
rm(time_y)
}

rm(Cluster.names)
rm(clusterID)



```








